---
title: "Stat 151A Final Project EDA"
author: "Andre Sha"
date: "12/9/2020"
output: pdf_document
---


```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(usmap)
library(ggplot2)
library(dplyr)
library(tidyr)
library(stringr)
library(reshape2)
library(corrplot)
library(car) #VIF
library(gridExtra)
library(cowplot)
library(forecast)
```

DataSet

https://data.world/nrippner/cancer-linear-regression-model-tutorial

```{r}
cancer <- read.csv("Data/cancer_reg.csv")
# U.S. Department of Agriculture
## https://www.nrcs.usda.gov/wps/portal/nrcs/detail/national/home/?cid=nrcs143_013697
fips_codes <- read.csv("Data/FIPS_codes.csv")
state_abbr <- read.csv("Data/State_Abbreviation_Mapping.csv") 
```

```{r}
# remove columns with null values
cancer_cleaned <- subset(cancer, select=-c(PctSomeCol18_24, PctEmployed16_Over, 
                                   PctPrivateCoverageAlone)) 
# PctSomeCol18_24 had 2285 missing values
# PctEmployed16_Over had 152 missing values
# PctPrivateCoverageAlone had 609 missing values

names(cancer_cleaned) # Feature names
dim(cancer_cleaned) # Matrix dimensions
head(cancer_cleaned)
```

```{r}
# Map Geopgrahy to County Name and State Columns, fix formatting for future join
County <- sub(",.*$", "", cancer_cleaned$Geography)
State <- sub("^.*,\\s*", "", cancer_cleaned$Geography)

# Clean County for join with FIPS
empty_subs = c(" County", " Parish", " City and Borough", 
               " Municipality", " Borough", " Census Area")
for (sub_string in empty_subs) {
  County <- sub(sub_string, "", County) 
}
County <- sub("city", "City", County) 
County <- sub("St ", "St. ", County) 

# Create New columns
cancer_cleaned$County<- County
cancer_cleaned$State <- State
cancer_cleaned <- subset(cancer_cleaned, select = -c(Geography)) # Redundant

# Map State Abbreviation to Full Name
fips_codes$County <- sub("St ", "St. ", fips_codes$County) 
fips <- merge(fips_codes, state_abbr[, c('State', 'Postal.Abbreviation')], 
      by.x='State', by.y='Postal.Abbreviation', all.x=TRUE)
fips <- fips %>% 
  rename(
    State.Abbreviation = State,
    State = State.y
    )
```


```{r}
# Join FIPS Info
mydata <- left_join(cancer_cleaned, fips, by=c('County', 'State'))
mydata <- mydata %>% 
  rename(
    fips = FIPS,
    state = State
    )
head(mydata)
```

```{r}
# Plot Target Rate by County
plot_usmap(data = mydata, values = "TARGET_deathRate") + 
  scale_fill_continuous(low = "white", high = "red",
                name = "Death Rate", label = scales::comma) + 
  theme(legend.position = "right")
```

```{r}
head(mydata)
```


```{r}
# Plot Target Rate by State
state_grouped <- mydata %>%
	group_by(state) %>%
	summarise(
	  TARGET_deathRate = mean(TARGET_deathRate),
	  PctPrivateCoverage = mean(PctPrivateCoverage),
	  BirthRate = mean(BirthRate)
	  )

plot_usmap(data = state_grouped, values = "TARGET_deathRate") + 
  scale_fill_continuous(low = "white", high = "red",
                name = "Death Rate", label = scales::comma) + 
  theme(legend.position = "right")
```

# Added in more Plots per Miyabi recommendation

```{r}
# Plot PctWhite Rate by State
plot_usmap(data = state_grouped, values = "BirthRate") + 
  scale_fill_continuous(low = "white", high = "blue",
                name = "Birth Rate", label = scales::comma) + 
  theme(legend.position = "right")
```

```{r}
# Plot PctPrivateCoverage Rate by State
plot_usmap(data = state_grouped, values = "PctPrivateCoverage") + 
  scale_fill_continuous(low = "white", high = "green",
                name = "Private Coverage", label = scales::comma) + 
  theme(legend.position = "right")
```


# EDA

Things to do: 

Since we have multiple variables for regression, we'd want to detect multicollinearity within our regressors. 
https://online.stat.psu.edu/stat462/node/180/

```{r}
head(mydata)
```
```{r}
geography = subset(mydata, select = c("County","state", "State.Abbreviation","fips"))

df <- mydata[,c(1:30)]
str(df)

#Goal: take each row of binned income, and find mean between its lower and upper decile. 

head(df$binnedInc)

#From stringr package:

df$binnedInc <- str_replace(df$binnedInc, "[(]", "")
df$binnedInc <- str_replace_all(df$binnedInc, "[)]", "")
df$binnedInc <- gsub("\\[|\\]", "", df$binnedInc)
#df$binnedInc <- strsplit(df$binnedInc, ',')
df$binnedInc <- sapply(strsplit(df$binnedInc, ','), function(x) mean(as.numeric(x)))
df$binnedInc
head(df)


```
Next on to do list, remove outliers by checking boxplot quartiles. 

- Do we remove outliers in our dependent variable? 

```{r}
cor(df)
```
```{r}
heatmap(cor(df), scale="column")

```
Fuck this is ugly

```{r}
cormat <- round(cor(df),2)
head(cormat)
melt(cormat)
library(ggplot2)
ggplot(data = melt(cormat), aes(x=Var1, y=Var2, fill=value)) + 
  geom_tile()
```

```{r}
corrplot(cor(df), method = "circle")

```

```{r}
 #matrix of the p-value of the correlation 
p.mat <- cor.mtest(df)$p
corrplot(cor(df), type = "upper", order = "hclust", tl.pos = "td", tl.cex = 0.5, method = "color", 
         p.mat = p.mat, sig.level = 0.1, insig = "blank")
```
We note at the top right side of the correlation plot there is multicollinearity between the variables.

- Add Final table for all removed or cleaned variables

http://www.sthda.com/english/articles/39-regression-model-diagnostics/160-multicollinearity-essentials-and-vif-in-r/

```{r}
full_model <- lm(TARGET_deathRate ~., data = df)
vif <-car::vif(full_model)
#variance inflation factor tells us that the variance of the popEst2015 coefficient is inflated by a factor of 26.43 because popEst2015 is highly correlated with at least one of the other predictors in the model.

vif
```
There's no specific cutoff, but based on https://stats.stackexchange.com/questions/342161/how-do-i-know-what-my-vif-limits-should-be-for-collinearity-should-be-when-doing/342181, a cut-off value of 10 seems plausible? 

- Fox Chapter 13: 341, 358

```{r}
remove_features <- vif[vif > 10]
remove_features
```

```{r}
names(vif[-remove_features])
```

```{r}
df2 <- df[,names(vif[-remove_features])]
df2
```
#Next up, whether or not these values r normally distributed. If not -> Log transformation? 

skeleton code: 
for (i in ncol(df)){
        gghist(df[i])
}

```{r}
p <- 
for (i in 1:ncol(df2)){
print(ggplot(df2, aes(x=df2[,i])) + 
  geom_histogram(color="black", fill="grey", bins = 10) +
  geom_vline(aes(xintercept = mean(df2[,i])),
             color = 'blue', size = .5)) +
  geom_rug(sides = 'b')

}


#Things to do: Grid arrange plots



```

```{r}
for (i in 1:ncol(df2)){
  lambda <- BoxCox.lambda(df2[,i])
  df2[,i] <- BoxCox(df2[,i], lambda)
}
```

We will perform boxcox transformation on everything. 
```{r}
#df2[,"popEst2015"] <- log(df2[,"popEst2015"])
#df2[,"PctBachDeg25_Over"] <- log(df2[,"PctBachDeg25_Over"])
#df2[,'PctPrivateCoverage'] <- (df2[,"PctPrivateCoverage"])**2
#lambda <- BoxCox.lambda(df2[,'PctWhite'])
#df2[,'PctWhite'] <- BoxCox(df2[,'PctWhite'], lambda)

```


```{r}
ggplot(df, aes(x=df2[,'popEst2015'])) + 
  geom_histogram(color="black", fill="grey") +
  geom_vline(aes(xintercept = mean(df2[,'popEst2015'])),
             color = 'blue', size = .5)

ggplot(df, aes(x=df2[,"PctBachDeg25_Over"])) + 
  geom_histogram(color="black", fill="grey") +
  geom_vline(aes(xintercept = mean(df2[,"PctBachDeg25_Over"])),
             color = 'blue', size = .5)

ggplot(df, aes(x=df2[,'PctPrivateCoverage'])) + 
  geom_histogram(color="black", fill="grey") +
  geom_vline(aes(xintercept = mean(df2[,'PctPrivateCoverage'])),
             color = 'blue', size = .5)

ggplot(df, aes(x=df2[,'PctWhite'])) + 
  geom_histogram(color="black", fill="grey") +
  geom_vline(aes(xintercept = mean(df2[,'PctWhite'])),
             color = 'blue', size = .5)

```
```{r}
head(df2)
```
```{r}
p <- 
for (i in 1:ncol(df2)){
print(ggplot(df2, aes(x=df2[,i])) + 
  geom_histogram(color="black", fill="grey", bins = 10) +
  geom_vline(aes(xintercept = mean(df2[,i])),
             color = 'blue', size = .5)) +
  geom_rug(sides = 'b')

}


```

```{r}
df2$TARGET_deathRate = df$TARGET_deathRate

```

